Establishing Trusted I/O Paths for Client \\ Shielded Execution Systems with Aurora

### 2019-07-04 abstract/abstract.tex
refresh reviewers' comments

To this end, we propose a novel architecture called \textsc{Aurora} to provide trusted I/O paths for enclave programs even in the presence of untrusted system software.
Specifically, \textsc{Aurora} exploits two commercial-off-the-shelf x86 platform features (System Management Mode, SMM and SGX) and establishes a secure channel between an enclave program and target device.
Furthermore, we design and implement trusted paths for HID keyboard, serial port printer, hardware clocks, and USB mass storage, respectively. Leveraging these trusted paths, we protect real-world applications including OpenSSH client, OpenSSL server/client and SQLite database.
Security evaluations show that \textsc{Aurora} mitigates several kinds of I/O related attacks. Performance evaluations demonstrate that \textsc{Aurora} introduces acceptable overheads.

>>>>

To this end, we propose a novel architecture called \textsc{Aurora} to provide trusted I/O paths for enclave programs even in the presence of untrusted system software.
Specifically, \textsc{Aurora} exploits two commercial-off-the-shelf features (System Management Mode, SMM and SGX) and establishes a secure channel between an enclave program and target device.
Furthermore, we design and implement trusted paths for HID keyboard, serial port printer, hardware clocks, and USB mass storage, respectively. Leveraging these trusted paths, we protect real-world applications including OpenSSH client, OpenSSL server/client and SQLite database.
Security evaluations show that \textsc{Aurora} mitigates several kinds of I/O related attacks. Performance evaluations demonstrate that \textsc{Aurora} introduces acceptable overheads.

### 2019-07-04 article.tex
refresh reviewers' comments

% Author(s) Name
\author{Hongliang~Liang,~\IEEEmembership{Member,~IEEE,}
	Mingyu Li,~Yixiu Chen,~Lin Jiang,~Zhuosi Xie,~Tianqi Yang\\
	Trusted Software and Intelligent System Lab\\
	Beijing University of Posts and Telecommunications
	\thanks{H. Liang, M. Li, Y. Chen, L. Jiang, Z. Xie, T. Yang
  are with Beijing University of Posts and Telecommunications, Beijing 100876, China. e-mail: (\{hliang,maxul,jianglin,xiezhuosi,yangtianqi,chenyixiu\}@bupt.edu.cn)
  }% <-this % stops a space
}

>>>>

% Author(s) Name
\author{Hongliang~Liang,~\IEEEmembership{Member,~IEEE,}
	Mingyu Li,~Yixiu Chen,~Lin Jiang,~Zhuosi Xie,~Tianqi Yang\\
	%\{hliang, maxul, chenyixiu, jianglin, xiezhuosi, yangtianqi\}@bupt.edu.cn\\
	%Trusted Software and Intelligent System Lab\\
	%Beijing University of Posts and Telecommunications
	\thanks{H. Liang, M. Li, Y. Chen, L. Jiang, Z. Xie, T. Yang are with Trusted Software and Intelligent System Lab, Beijing University of Posts and Telecommunications, Beijing 100876, China. e-mail: (\{hliang, maxul, chenyixiu, jianglin, xiezhuosi, yangtianqi\}@bupt.edu.cn) }% <-this % stops a space
    \thanks{This work was supported by the National Natural Science Foundation of China (NSFC) under Grant No. U1713212 and 91418206.}
}
